%!TEX root = touchdevelop_tutorials.tex
\section{Method}

To conduct our study, we used the public TouchDevelop API to extract 35000 scripts which we stored in a MySQL database.

\subsection{Analysis}

We used SQL queries and statistical methods to examine our data.

As our data tended to be heavily skewed to the left, we used non-parametric statistics, such as Kruskal-Wallis.

\note{Please verify} To identify a script as a tutorial, we... (describe how we identified the initial tutorial script. Was it that we went to the web site and then looked at the site? Or, based on naming? Or something else?)

\note{Sergii please verify} Scripts (**that users create as a result of following a tutorial**???**) are tagged with \texttt{\#doc}, \texttt{\#tutorials}, or \texttt{\#interactiveTutorial} in the case of an interactive tutorial.


We identified that tutorials were tagged with the \#doc hashtag and that there are a total of XX tutorials.

\boldnote{When appropriate, we removed some usernames from our analysis.}
We contacted the TouchDevelop team and learned further that certain author names, including ``TouchDevelop Samples'' and ``TouchDevelop Documentation'', were operated by Microsoft employees; in our author data analysis we remove these from the analysis. \note{Be really specific when we actually do this. we might have to rewrite this statement}

\note{There are some group accounts based on the account name and activity. We cannot be certain, however, we can only guess and this has to be a threat to validity.}